Abstractions for Type-Level Programming

### 2022-04-21 article.tex
Do TODO

An important limitation of \SystemFm compared to Scala's type system is that it does not support empty types.
The bottom of Scala's subtyping lattice, called |Nothing|, provides a direct way to refer to empty sets of values.
Intersection types also provide a way to construct uninhabited types given that Scala does not forbid intersecting two disjoint types.
Empty types are problematic for the match type reduction algorithm as they break the fundamental assumption that two types cannot be both disjoint and subtypes (\Cref{lem:disjointness-subtyping-exclusivity}).
To account for this, our implementation uses an additional \emph{inhabitance check} on scrutinee types before attempting any reduction.

@@

% TODO: tell the truth about empty types

>>>>

An important limitation of \SystemFm compared to Scala's type system is that it does not support empty types.
The bottom of Scala's subtyping lattice, called |Nothing|, provides a direct way to refer to empty sets of values.
Intersection types also provide a way to construct uninhabited types given that Scala does not forbid intersecting two disjoint types.
Empty types are problematic for the match type reduction algorithm as they break the fundamental assumption that two types cannot be both disjoint and subtypes (\Cref{lem:disjointness-subtyping-exclusivity}).
To account for this, our implementation uses an additional \emph{inhabitance check} on scrutinee types before attempting to prove types disjoint.
This updated definition of disjointness allows us to maintain the property of \Cref{lem:disjointness-subtyping-exclusivity} in the presence of empty types (disjointness/subtyping exclusivity).

@@
